RSV

### 2018-01-12 Analysis/RSV.Rmd
Updated to outbreakpredict 0.3

    countyYearPred = countyYearModel %>% 
      predict(type="response", newdata=modelTime, se.fit=TRUE)

    countyYearPred = modelTime %>% 
      cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
      rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

@@

    countyYearThresholds = countyYearModel %>%
      outbreak.predict.scalars(
        modelTime,
        function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
      ) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

@@

    if (y %in% rsvWindowYears) {
      countyYearUnprotectedSim = countyYearModel %>%
        outbreak.predict.scalars.sim(
          modelTime,
          function(model, params, newdata) { 
            outbreak.calc.unprotected(model, params, newdata$time, ppxSlidingStrategies(c, y))
          }
        ) %>%
        mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

>>>>

    countyYearPred = countyYearModel %>% 
      predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)

    countyYearPred = data.frame(time=modelTime) %>% 
      cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, outbreak.calc.cum())) %>%
      rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

@@

    countyYearThresholds = countyYearModel %>%
      outbreak.predict.scalars(
        modelTime,
        outbreak.calc.thresholds(onset=seasonThreshold, offset=1 - seasonThreshold)
      ) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

@@

    if (y %in% rsvWindowYears) {
      countyYearUnprotectedSim = countyYearModel %>%
        outbreak.predict.scalars.sim(
          modelTime,
          outbreak.calc.unprotected(ppxSlidingStrategies(c, y))
        ) %>%
        mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)
